\documentclass[10pt,a4paper]{article}
\usepackage{enumitem}
\usepackage[margin=0.5in]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{hhline}
\pagenumbering{gobble}
%The following will ensure that the PDF output will be all unicode and machine-readable.
\input{glyphtounicode}
\pdfgentounicode=1

\graphicspath{ {images/} }
\titleformat*{\section}{\normalsize \bfseries}
\titlespacing\section{0pt}{5pt}{5pt}
\urlstyle{same}
\def\Plus{\texttt{+}}

\begin{document}

\begin{center}
{\bf \Large Hiten Pragji\\} \href{https://www.linkedin.com/in/hkpragji/} \faLinkedin \space \href{https://github.com/hkpragji} \faGithub \\
\textbf{\faLocationArrow \space London |  \faPhone \space 07450 217119 | \faEnvelope \space \href{mailto:hkpragji@gmail.com}{hkpragji@gmail.com}}
\end{center}

\hrule

\section*{\faUser\space\bf Summary}
\noindent Highly numerate statistical data analyst and physics graduate currently working as a data specialist. Confident using SQL, R, and Power BI; interested in applying mathematical methods and analytics and visualisation tools to drive successful data-driven decision making. Looking to apply and further develop my knowledge and skills in analytics and data science.\\

\hrule

\section*{\faCog\space\bf Skills}
\begin{itemize}[leftmargin=*,align=left]
\normalfont
\item $\geq$ 5 years: Advanced Mathematics, Statistics, Excel, LaTeX.
\item $\leq$ 2 years: SQL, R, Power BI.
\end{itemize}

\hrule

\section*{\faLaptop\space\bf Training}

\begin{itemize}[leftmargin=*,align=left]
\normalfont
\item Advanced Statistics for Data Science (Coursera) - In progress
\item Data Analysis with R Programming (Coursera) - July 2023
\item Intermediate SQL for Data Scientists (LinkedIn Learning) - March 2023
\item Querying Microsoft SQL Server 2022 (LinkedIn Learning) - Feb. 2023
\item Microsoft SQL Server 2022 Essential Training (LinkedIn Learning) - Dec. 2022
\item Power BI Essential Training (LinkedIn Learning) - Nov. 2022
\end{itemize}

\hrule

\section*{\faGraduationCap\space\bf Education}

\noindent \textbf{MSc Medical Physics - Distinction - University of Surrey, 2019-21}
\begin{itemize}[leftmargin=*,align=left]
\normalfont
\item Distinction (82$\%$) in the Research Project and Dissertation, ``Understanding SARS-CoV-2 and the impacts of associated variants of concern on the COVID-19 pandemic''. Awarded the 2021/2 IPEM Student Prize for outstanding performance in the MSc Medical Physics programme dissertation.
%\item Relevant modules: Experimental and Professional Skills for Medical Physics, Extended Group Project including Monte Carlo radiation transport modelling on the Linux operating system.%
\end{itemize}

\noindent \textbf{BSc (Hons) Theoretical Physics - 2:2 - Queen Mary University of London, 2014-18}
\begin{itemize}[leftmargin=*,align=left]
\normalfont
\item Distinction (72$\%$) in Extended Independent Project, ``An investigation into the spectral separation of semiconductor quantum dots for super-resolution microscopy.''
%\item Relevant modules: Scientific Measurement, Introduction to C\Plus\Plus\ Programming.%
\end{itemize}

\hrule

\section*{\faBriefcase\space\bf Experience}

\noindent \bf Data Specialist - UK Health Security Agency, Apr. 2023 - Present

\begin{itemize}[leftmargin=*,align=left]
\normalfont
\item Led the extract-transform-load (ETL) process for the development of Power BI reports; worked with the senior software developer to write advanced SQL scripts to migrate data between databases.
\item Transformed data in Power BI, derived statistical metrics, created advanced visualisations in R using the tidyverse package, and designed data tables for reports using DAX.
\item Prepared scientific reports and analysed them in Excel and R; communicated key findings, including statistical inaccuracies, to ensure scientific validity and completeness of data.
\item Developed R code to perform statistical hypothesis testing (specifically, the Kolmogorov-Smirnov test) on univariate datasets using various statistical packages.
\item Automated several administrative processes such as splitting, merging, and bulk renaming files using file manipulation packages in R.
\end{itemize}

\noindent \bf Data Quality Analyst - IQVIA, Nov. 2022 - Mar. 2023

\begin{itemize}[leftmargin=*,align=left]
\normalfont
\item Reinforced and built on the existing data quality framework by supporting the automation of the quality assurance process for management information (MI) deliverables (Power BI dashboards and reports); this involved writing SQL queries and collaborating with software developers to integrate SQL Server data into Power BI to track fluctuations in key metrics.
\item Supported agile methodology by pro-actively participating in the work-stream planning process which included daily scrum calls with the MI team, following each task through its life cycle, developing strong connections with colleagues.
\end{itemize}
\newpage
\noindent \bf Data Officer - NHS Digital, Jun. 2022 - Sep. 2022

\begin{itemize}[leftmargin=*,align=left]
\normalfont
\item Managed the extract-transform-load (ETL) process for five national cancer datasets, ensuring the availability of high-quality (clean and complete) data for disease registration, in line with standard operating procedures and strict deadlines.
\item Performed quality assurance and validation for five national cancer datasets; communicated with internal stakeholders and NHS Trusts to resolve data quality issues. Ensured data was received in agreed formats, in line with service level agreements.
\item Analysed data transformation mappings to diagnose and solve compatibility issues between the source data and the data warehouse, ensuring that different data formats were integrated correctly into the ETL system.
\end{itemize}

\noindent \bf Data Administrator - UK Health Security Agency, Feb. 2019 - May 2022

\begin{itemize}[leftmargin=*,align=left]
\normalfont
\item Increased the effectiveness of the COVID-19 pandemic response and accelerated turnaround times for test reports by assisting in testing and deploying a VBA application to import COVID-19 patient data and diagnostic data into the laboratory information management system (LIMS).
\item Efficiently and accurately updated the LIMS and resolved data validation issues through effective communication with internal and external stakeholders.
\end{itemize}

\end{document}